Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

This inclusion of university-provided messaging applications in the survey might
explain why there are so few teachers, just 6.7\%, that answered they did not
use any messaging application. In general, universities provide official
channels to send (or simply make available to) students academic information
such as the exam schedule or the grades. The statistical mode is to use that
kind of messaging. Some other teaching staff might not use it, but use some
extraofficial or opt-in channels such as the others included in the survey; in
the end, between these official and extra-official channels, most people cover
their needs to communicate with students. This matches the subjective experience
of the authors of this paper, in general.

Furthermore, the answers to the survey question regarding COVID highlights the
significant challenge of altering behavior, even during a major crisis. Very few
responders actually changed their habits, although comparing women vs. men as
well as those teaching social sciences vs. the rest of the disciplines, there
are some significant differences. We do not have a clear understanding of the
reasons behind this behavior; however, it appears that the perception and
adoption of technologies in a major crisis may vary based on an individual's
background and gender.

>>>>

This inclusion of university-provided messaging applications in the survey might
explain why there are so few teachers, just 6.7\%, that answered they did not
use any messaging application. In general, universities provide official
channels to send (or simply make available to) students academic information
such as the exam schedule or the grades. The statistical mode is to use that
kind of messaging application. Some other teaching staff might not use it, but use some
extraofficial or opt-in channels such as the others included in the survey; in
the end, between these official and extra-official channels, most people cover
their needs to communicate with students. In general, this matches the subjective experience
of the authors of this paper.

Furthermore, the answers to the survey question regarding COVID-19 highlights the
significant challenge of altering behavior, even during a major crisis. Very few
responders actually changed their habits, although comparing women vs. men as
well as those teaching social sciences vs. the rest of the disciplines, there
are some significant differences. We do not have a clear understanding of the
reasons behind this behavior; however, it appears that the perception and
adoption of technologies in a major crisis may vary based on an individual's
background and gender.
